Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them

### 2020-11-26 Manuscript/EPAWTFT.tex
35 and 45

%%%%%%%%%%%%%%%%%
\begin{figure}
    \includegraphics[width=\linewidth]{PadeRMP}
    \caption{\label{fig:PadeRMP}
    RMP ground-state energy as a function of $\lambda$ obtained using various resummation techniques at $U/t = 4.5$.}
\end{figure}
%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%
\begin{figure*}
    \includegraphics[height=0.23\textheight]{PadeRMP35}
    \includegraphics[height=0.23\textheight]{PadeRMP45}
    \caption{\label{fig:PadeRMP}
    RMP ground-state energy as a function of $\lambda$ obtained using various resummation techniques at $U/t = 3.5$ (left) and $U/t = 4.5$ (right).}
\end{figure*}
%%%%%%%%%%%%%%%%%
